TBD

### 2021-03-07 outputs/paper/paper.Rmd
update

```{r }
library(randomForest)
library(plyr)

map(dat, ~sum(is.na(.)))

set.seed(123)
FS<-randomForest(post_favor_Sanders~., data=dat, ntree=500)
FS_importance <- importance(FS)
FS_varImportance <- data.frame(Variables = row.names(FS_importance), 
                            Importance = FS_importance[ ,'MeanDecreaseGini'])
FS_varImportance <- as.data.frame(FS_varImportance)
max(FS_varImportance$Importance)
FS_varImportance_sort <- arrange(FS_varImportance,desc(Importance))

@@

>>>>

```{r fs, fig.width=10, fig.height=10 }
library(randomForest)
library(plyr)
# deal with missing value
FS<- dat%>%
select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt,exp_2_prompt,post_favor_Klobuchar,post_favor_Warren,post_favor_Biden,post_favor_Bloomberg,exp_2,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7))%>%
na.omit()

set.seed(123)
FS_tree<-randomForest(post_favor_Sanders~., data=FS, ntree=500)
FS_importance <- importance(FS_tree)
FS_varImportance <- data.frame(Variables = row.names(FS_importance), 
                            Importance = FS_importance[ ,'MeanDecreaseGini'])
FS_varImportance <- as.data.frame(FS_varImportance)
max(FS_varImportance$Importance)
FS_varImportance_sort <- arrange(FS_varImportance,desc(Importance))

@@

## missing value
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, fig.width=10, fig.height=10}
library("VIM")
aggr(dat,prop=FALSE,numbers=TRUE)
